\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed

### 2015-07-10 paper/figure3.tex
MT Summit, just before adding Isabel's latest

\begin{figure*}[t]
\begin{subfigure}[b]{.5\linewidth}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={0,1,2,3,4,5,6},
    xticklabels={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

@@

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{subfigure}
\begin{subfigure}[b]{.5\linewidth}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4},
    xticklabels={PE7,PE8,PE9,PE10},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

@@

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure*}

>>>>

\begin{figure}
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[%scale only axis=true, width=80mm, height=73mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={0,1,2,3,4,5,6},
    xticklabels={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

@@

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{center}
\end{subfigure}
\ \\ \ \\
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[%scale only axis=true, width=60mm, height=73mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4},
    xticklabels={PE7,PE8,PE9,PE10},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

@@

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\end{center}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure}

### 2015-07-10 paper/paper_abstract.tex
MT Summit, just before adding Isabel's latest

\begin{abstract}
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
%
We select two news articles, and ask six Russian-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
%
We obtain human adequacy judgements of the post-edited sentences, 
%
%and demonstrate
%along with human adequacy judgements for the unedited machine translations and the monolingual post-edited translations of \citet{2014_WMT_Schwartz_etal}.
%
%In this work, we 
and demonstrate that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%We also find that monolingual post-edited translations are 
%
%In this work, we confirm prior work indicating that bilingual 
%
%As part of the Workshop on Statistical Machine Translation, \citet{2014_WMT_Schwartz_etal} examined the extent to which monolingual native English speakers were able to post-edit machine translation of news articles into fluent, adequate English translations of Russian source sentences.
%
\end{abstract}

>>>>

\begin{abstract}
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
%
We select four news articles, and ask six Russian-English bilinguals and four Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
%
We obtain human adequacy judgements of the post-edited sentences, 
%
%and demonstrate
%along with human adequacy judgements for the unedited machine translations and the monolingual post-edited translations of \citet{2014_WMT_Schwartz_etal}.
%
%In this work, we 
and demonstrate that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%We also find that monolingual post-edited translations are 
%
%In this work, we confirm prior work indicating that bilingual 
%
%As part of the Workshop on Statistical Machine Translation, \citet{2014_WMT_Schwartz_etal} examined the extent to which monolingual native English speakers were able to post-edit machine translation of news articles into fluent, adequate English translations of Russian source sentences.
%
\end{abstract}

### 2015-07-10 paper/paper_conclusion.tex
MT Summit, just before adding Isabel's latest

Our results indicate that, at least for this language pair and this data set, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%Our results indicate that this finding holds across participants and across segments of varying MT quality. 
%
This result holds across participants, and is strongest when MT quality is poor.

>>>>

%The question of how a post-editing interface should be configured and presented to users is a fundamentally interdisciplinary and empirical one.
%
%Issues of user interface design, human factors, translation studies, and machine translation quality are all likely relevant.
%
%Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
%In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.

In this work, we observe that when machine translation quality is poor, bilingual post-editors may produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.
%
%Alternatively, when machine translation quality is high, no effect is seen by presenting alignment visualizations.
%
We explain this by hypothesizing that word alignment visualization may enable post-editors to better recover from certain types of translation errors produced by MT systems; when MT quality is high enough that such errors are absent, word alignment visualization may no longer play a restorative role.
%
The timing results we observe, while not statistically significant, appear to be consistent with prior work that found per word post-editing times to be shorter for segments that were less cognitively demanding.

%This work begins an attempt to answer two novel questions regarding post-editing interface design: 
%%
%To what extent, if at all, does the presentation of source-to-target word-level alignment links affect the quality or speed of post-editing?
%%
%Is any such effect, if it exists, dependent on certain aspects of machine translation quality, or on the language pair?

%Our results indicate that, at least for this language pair and this data set, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%Our results indicate that this finding holds across participants and across segments of varying MT quality. 
%
%This result holds across participants, and is strongest when MT quality is poor.

### 2015-07-10 paper/paper_intro.tex
MT Summit, just before adding Isabel's latest

Small-scale studies have suggested that monolingual human post-editors, working without knowledge of the source language, can also improve the quality of machine translation output \citep{2005_NIST_CallisonBurch,2010_NAACL_Koehn,2013_WPTP_Mitchell_etal}, especially if well-designed tools provide automated linguistic analysis of source sentences \citep{2009_EACL_Albrecht_etal}.
%
\citet{2014_WMT_Schwartz_etal} confirmed this result with eight monolingual post-editors on a larger 3000 sentence test corpus.
%
\citet{2014_WPTP_Schwartz} demonstrated that a monolingual post-editor who is a domain expert in the translated material can successfully post-edit.

In this work, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}), in which six Russian-English bilingual translation students were asked to post-edit news articles that were previously machine translated from Russian into English.
%
We find (\S\ref{sec:results}) that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.

>>>>

The question of how a post-editing interface should be configured and presented to users is a fundamentally interdisciplinary and empirical one.
%
Issues of user interface design, human factors, translation studies, and machine translation quality are all likely relevant.
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.

This work begins an attempt to answer two novel questions regarding post-editing interface design: 
%
To what extent, if at all, does the presentation of source-to-target word-level alignment links affect the quality or speed of post-editing?
%
Is any such effect, if it exists, dependent on certain aspects of machine translation quality, or on the language pair?

To address these questions, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}) where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.
%
In the first condition, we ask six Russian-English bilingual translation students to post-edit two Russian language news articles starting with relatively low quality English machine translation.
%
In the second condition, we ask four Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
%
We find (\S\ref{sec:results}) that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
We find no statistically significant effect when machine translation quality is high.
%
We also found that for both Russian-English and Spanish-English the mean post-editing times were shorter for texts with alignment than for texts without alignment. These differences were not significant, but the difference for the Russian-English texts approached significance. 
%
Finally, in \S\ref{sec:background} we briefly survey the current state of post-editing research and situate this work within the context of related work in post-editing.

### 2015-07-10 paper/paper_methodology.tex
MT Summit, just before adding Isabel's latest

\begin{table*}[t]
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  12 & The post-edited translation is superior to the reference translation \\ \hline
  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Russian-English}
\label{judge_guidelines_russian}
\end{subtable}
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
%  9 & The English translation contains one minor error \\ \hline
  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Spanish-English}
\label{judge_guidelines_spanish}
\end{subtable}
\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges \citep{2009_EACL_Albrecht_etal}. Because no reference translation was available for Spanish-English, the 12 category is omitted.}
\label{judge_guidelines}
\end{table*}

\subsection{Russian-English Bilingual Participants}
There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

There were four participants (PE7, PE8, PE9, PE10) who served as post-editors in this portion of the study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals with English as their first language (L1) and highly proficient in Spanish as their second language (L2). 
%
The four were second year students in a university Master of Spanish Translation program.

\subsection{Russian Data}

We selected as source texts a subset of the texts from the 2014 Workshop on Statistical Machine Translation (WMT-14) shared translation task \citep{2014_WMT_Bojar_etal}.
%
Source texts were news articles covering world news events in late 2013.
%
The first text (Doc A) was originally a Russian-language BBC news article covering Syrian chemical weapons.
%
The second text (Doc B) was originally an English-language news article covering U.S. spying policy.
%
The texts were divided into segments that corresponded to sentences or stand-alone phrases (typically corresponding to news headlines, captions, or cutlines).
%
Segments in Doc A varied in length from 3 to 35 words (mean length 17 words); 
%
segments in Doc B varied in length from 9 to 55 words (mean length 23 words).

Professional translations of Doc A into English and Doc B into Russian were commissioned as part of the WMT-14 shared translation task \citep{2014_WMT_Bojar_etal}.
%
%Doc A consists of 27 segments; Doc B has 28 segments.
%
The Russian version of each text was translated automatically using Moses \citep{2007_ACL_Koehn} by \citet{2014_WMT_Schwartz_etal} as part of their WMT14 shared task submission.
%
As a side effect of the phrase-based MT process, Moses can be configured to produce alignment links, indicating which target language words were produced from which source language words.
%
To enable maximal comparability with the post-editing results of \citet{2014_WMT_Schwartz_etal}, we make use of those machine translations and alignments in this work.

@@

\subsection{Spanish Data}

Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
%
The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
%
The first text (Doc C) had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text (Doc D) had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
%
No reference translations exist for either Spanish text.

The Spanish source texts were translated automatically using the Microsoft Bing Translator through its online developer API.
%
Bing Translator, when accessed via the developer API, can be configured to return character-level alignment links from source characters to target characters, in addition to  translated target language sentences.
%
Our scripts derive word alignments from the character alignments returned by the Bing Translator API.

\subsection{Russian-English Post-Editing Interface}

Each text was presented to post-editors in one of two variant modalities using the post-editing interface of \citet{2014_WMT_Schwartz_etal}. 
%
In both variants, each Russian source segment was presented along with the corresponding machine translated English segment; a text field (initially populated with the machine translated segment) where the post-editor could make changes was also presented.
%
In variant 1, the alignment links produced by Moses were graphically displayed, linking source words to their corresponding machine translated target words.
%
In variant 2, the alignment links were omitted from the visualization interface.

Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
%
and to edit the other text using the interface where alignment links were omitted.
%
Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
%
Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
%
Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using the variant 1 interface.

\subsection{Spanish-English Post-Editing Interface}

\input{figure1}

\subsection{Procedure}

@@

>>>>

We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlaying machine translations.
%
To test this hypothesis, we conduct a bilingual post-editing experiment  where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.

\input{paper_table}

\subsection{Bilingual Participants}

%All participants were bilingual graduate students enrolled in translations studies.

\subsubsection{Russian-English Bilingual Participants}
There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
We designate these participants as PE1--PE6.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

There were four participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals.
%
We designate these participants as PE7--PE10.
%
The first language (L1) of all four participants was English, and all four were highly proficient in Spanish as their second language (L2). 
%
These participants were second year students in a university Master of Spanish Translation program.

\subsection{Source Language Data}

\subsubsection{Russian Data}

For the Russian-English portion of this study, we selected as source texts a subset of the texts from the 2014 Workshop on Statistical Machine Translation (WMT-14) shared translation task \citep{2014_WMT_Bojar_etal}.
%
Source texts were news articles covering world news events in late 2013.
%
The first text was originally a Russian-language BBC news article covering Syrian chemical weapons.
%
The second text was originally an English-language news article covering U.S. spying policy.
%
We designate the former as Doc A and the latter as Doc B.

These two texts were each divided into segments (32 and 33 segments, respectively) that corresponded to sentences or stand-alone phrases (typically corresponding to news headlines, captions, or cutlines).
%
Segments in Doc A varied in length from 3 to 35 words (mean length 17 words); 
%
segments in Doc B varied in length from 9 to 55 words (mean length 23 words).

Professional translations of Doc A into English and Doc B into Russian were commissioned as part of the WMT-14 shared translation task \citep{2014_WMT_Bojar_etal}.
%
%Doc A consists of 27 segments; Doc B has 28 segments.
%
The Russian version of each text was translated automatically using Moses \citep{2007_ACL_Koehn} by \citet{2014_WMT_Schwartz_etal} as part of their WMT14 shared task submission.
%
As a side effect of the phrase-based MT process, Moses can be configured to produce alignment links, indicating which target language words were produced from which source language words.
%
To enable maximal comparability with the post-editing results of \citet{2014_WMT_Schwartz_etal}, we make use of Russian-English machine translation results and alignments from that work here.

\subsubsection{Spanish Data}

Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
%
The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
%
The first text had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
%
We designate the former as Doc C and the latter as Doc D.
%
No reference translations exist for either Spanish text.

The Spanish source texts were translated automatically using Microsoft Bing Translator through its online developer API.
%
Bing Translator, when accessed via the developer API, can be configured to return character-level alignment links from source characters to target characters, in addition to  translated target language sentences.
%
Our scripts derive word alignments from the character alignments returned by the Bing Translator API.

\subsection{Translation Quality}
\label{sec:translation_quality}

We hypothesize that any effects of word alignment visualization on post-editing may be dependent on the quality of the underlying machine translations displayed to the post-editors.
%
Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.
%
Instead, following \citet{2009_EACL_Albrecht_etal} and \citet{2014_WMT_Schwartz_etal}, we therefore obtained human judgements of translation adequacy for the Russian-English and Spanish-English machine translations used in this study.

The Russian language news articles used in this study have corresponding reference translations.
%
It is therefore possible (although given current machine translation quality, highly unlikely) that machine translation quality for any given segment could conceivably surpass the quality of the corresponding reference translation (if for example, the reference translator makes a mistake).
%
For assessing the quality of the Russian-English machine translations, then, we follow the 12-point adequacy scale of \citet{2014_WMT_Schwartz_etal}.
%
This adequacy scale is shown in Table \ref{judge_guidelines_russian} \vpageref[above]{judge_guidelines_russian};
%
this scale ranges from a low of 2 (the English translation makes no sense at all) to a high of 12 (the translation is superior to the reference).

The Spanish language news articles used in this study lack corresponding reference translations.
%
Thus, unlike the case of our Russian data, no matter how high the quality of machine translations, no Spanish-English machine translation segment could possibly receive a score of 12.
%
For Spanish-English, we therefore follow the 10-point adequacy scale of \citet{2009_EACL_Albrecht_etal}.
%
This adequacy scale is shown in Table \ref{judge_guidelines_spanish} \vpageref[above]{judge_guidelines_spanish};
%
this scale is very similar to the former, but has a high of 10 (the meaning of the source sentence is fully conveyed in the English translation) instead of 12.

@@

\subsection{Post-Editing Interface}

For this study, we developed a novel post-editing interface, based on the open source software used and released by \citet{2014_WMT_Schwartz_etal}.
%
Our software is written using Scala \citep{2014_Scala_Odersky}, and is released as open source (see the software supplement that accompanies this work).
%
This code constitutes a ground-up rewrite of the Java-based post-editing interface of \citet{2014_WMT_Schwartz_etal}, written using a strict model-view-controller software design pattern to be easy for other researchers to use and extend.

Our post-editing interface can be seen in Figure~\ref{fig:screenshot_true} \vpageref[above]{fig:screenshot_true}.
%
Each text was presented to post-editors in one of two variant modalities --- word-level alignment links could either be visualized or left absent.
%
In both variants, each source language segment was presented along with the corresponding machine translated English segment; a text field (initially populated with the machine translated segment) where the post-editor could make changes was also presented.
%
In the first variant, the word-level alignment links produced by the machine translation decoder (Moses for Russian-English, Bing Translator for Spanish-English) were graphically displayed, linking source words to their corresponding machine translated target words.
%
In the second variant, the word-level alignment links were omitted from the visualization interface.

  \input{figure4}
 \subsection{Procedure}

@@

\subsubsection{Russian-English Participant Assignment}

Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
%
and to edit the other text using the interface where alignment links were omitted.
%
Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
%
Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
%
Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using variant 1.

\subsubsection{Spanish-English Participant Assignment}
